\let\nofiles\relax % This is because res says to not emit aux files,
                   % but lastpage needs aux files.
\documentclass[margin,line]{res}
\usepackage[colorlinks=true]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{amsmath,amssymb}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{etaremune}
\usepackage[normalem]{ulem}

\oddsidemargin -.5in
\evensidemargin -.5in
\voffset -25pt
%\topmargin -.2in
\headsep 25pt
\textwidth=6.0in
\textheight=9.4in
\itemsep=0in
\parsep=0in

% Headings
\pagestyle{fancy}
\lhead{Derrick Lee --- Resume}
\chead{}
\rhead{\thepage\ of \pageref*{LastPage}}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0.4pt}
%\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\newcommand{\myname}{Derrick Lee}
\newlength{\mynamewidth}
\settowidth{\mynamewidth}{\namefont\myname}

\name{\hspace*{0.5\textwidth}\hspace{-0.5\mynamewidth} \myname \vspace*{.1in}}
% On the first page, have no header.
\thispagestyle{empty}

\begin{resume}

\input{ContactContent.tex}

% \section{\sc Citizenship}
% United States

\section{\sc Education}
{\bf B.S., Computer Science (Math)} Santa Clara University \hfill {\bf June 2020} (expected)\\
Relevant Coursework:
\begin{itemize} \itemsep -2pt
  \item[-] Object Oriented Programming (C++)
  \item[-] Data Structures (C++)
  \item[-] Operating Systems (C/Rust)
  \item[-] Theory of Automata and Formal Languages (in progress)
%\item[ ] G.P.A.: 4.6/5.0
\end{itemize}

\section{\sc Experience}
  {\bf Open Source Developer} \hfill {\bf January 2018 - Present} \\
  \vspace{-3.5mm}
  \begin{itemize} \itemsep -2pt
    \item[-] Contributions to {\bf serenity},
    a {\bf Rust} library for interacting with the chat and VoIP platform Discord. 
    Fixed incomplete features, improved and clarified code examples and documentation.
    \item[-] Implemented bug fixes and security fixes to open source chat bot LuckyBot.
  \end{itemize}

\section{\sc Relevant Skills}
  {\bf Languages}
  \begin{itemize} \itemsep -2pt
    \item[ ] Rust, C, C++, JavaScript, TypeScript, Python, HTML5, CSS, ARM Assembly, SQL, Bash
  \end{itemize}
  {\bf Related Technologies}
  \begin{itemize} \itemsep -2pt
    \item[ ] Git, Node.js, GraphQL, PostgreSQL, React, Koa, Apollo, Express, Next.js, Vue.js
  \end{itemize}

\section{\sc Projects}

{\bf sushii-bot} (14,000+ lines of code) \hfill {\bf December 2017 -- Present} \\
  \vspace{-3.5mm}
  \begin{itemize} \itemsep -2pt
    \item[-] Chat bot for Discord with a ranking system, activity tracker, moderation tools and more with {\bf over 64,000 total users}.
    \item[-] Written in {\bf Rust} with a {\bf PostgreSQL} database, {\bf diesel-rs}, and connection pooling with {\bf r2d2-diesel}.
    \item[-] Paired a website with user leaderboards and statistics made with {\bf Next.js}, {\bf React}, {\bf Koa}, {\bf Apollo} server and client for {\bf GraphQL} endpoints,
      and {\bf Join Monster} for batch data fetching.
  \end{itemize}
{\bf Operating System Simulations} (5,000+ lines of code) \hfill {\bf April 2018 -- June 2018} \\
  \vspace{-3.5mm}
  \begin{itemize} \itemsep -2pt
    \item[-] Runs sequential and random disk reads with {\bf C}, determines time differences and possible causes based on both physical and OS aspects. 
      Programs and set up executed with {\bf Bash} scripts.
    \item[-] Multi threaded simulation written in {\bf Rust} of different memory page replacement algorithms with given page requests and a range of memory sizes. \
    Data visualized with plots made in {\bf R}.
    \item[-] Benchmarks in {\bf Rust} to determine the overhead of synchronization primitives (Mutex) and lock contention.
  \end{itemize}
{\bf vlive-rs} (1,000+ lines of code) \hfill {\bf April 2018 -- May 2018} \\
  \vspace{-3.5mm}
  \begin{itemize} \itemsep -2pt
    \item[-] {\bf Rust} library for livestreaming platform VLive's API to fetch channel and video data.
    \item[-] Implemented on the asynchronous {\bf Hyper} client with Futures as well as {\bf Reqwest} for a synchronous API.
  \end{itemize}
{\bf mp3-fft} \hfill {\bf July 2017} \\
  \vspace{-3.5mm}
  \begin{itemize} \itemsep -2pt
    \item[-] Web application that takes mp3 files and recommends 100+ headphones based on price, form factor, and
      music sound signature (bass-heavy, neutral, mid-forward, v-shaped).
    \item[-] Uses the Fourier Transform and Welch's method to classify sound signature.
    \item[-] Written in {\bf Python} with a {\bf Flask} microframework back-end along with {\bf Vue.js} for front-end.
  \end{itemize}

\end{resume}
\end{document}
