\documentclass{res} 

\usepackage{pifont}
\usepackage{multicol}
\usepackage{fancyhdr}
\newsectionwidth{0pt}  
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{24pt}
\setlength{\headsep}{24pt}
\pagestyle{fancy}
\cfoot{}
\topmargin=-0.6in

\begin{document}
	\thispagestyle{empty} % no header
	{\bf \huge{Derrick Lee}} \hfill {(408) 823-7288 | dlee3@scu.edu} \\
	\hspace*{\fill} {linkedin.com/in/drklee | github.com/drklee3} \\
	\hspace*{\fill} {drklee.me} \\
	\noindent\rule{\textwidth}{1pt}
	\begin{resume}

		\section{EDUCATION}

		{\bf Santa Clara University} \hfill {\bf September 2016 - June 2020 (Expected)} \\
			B.S. Computer Science \\
			Relevant Coursework:
			\vspace{-3.5mm}
			\begin{multicols}{2}
			\begin{itemize} \itemsep -2pt
				\item Intro to Computer Science
				\item Object Oriented Programming
				\item Data Structures
				\item Intro to Embedded Systems
			\end{itemize}
			\end{multicols}
		
		\section{RELEVANT SKILLS}
		\vspace{6pt}

			{\bf Languages:} JavaScript, Rust, Python, C++, HTML5, CSS, ARM Assembly, SQL \\
			{\bf Related Technologies:} Node.js, Koa, Apollo, GraphQL, PostgreSQL, React, Express, Next.js, Vue.js, jQuery

		\section{PROJECTS} 
		\vspace{6pt}

		{\bf sushii-bot} \emph{https://github.com/drklee3/sushii-bot} \hfill {\bf December 2017 - Present} \\
			\vspace{-3.5mm}
			\begin{itemize} \itemsep -2pt
				\item Chat bot with a ranking system, activity tracker, moderation tools, and more. 
				\item Written in {\bf Rust} with a {\bf PostgreSQL} database, {\bf diesel-rs}, and connection pooling with {\bf r2d2-diesel}.
				\item Paired a website with leaderboards and statistics.
				\item Website made with {\bf Next.js}, {\bf React}, {\bf Koa}, {\bf Apollo} server and client for {\bf GraphQL} endpoints,
					and {\bf Join Monster} for batch data fetching.
			\end{itemize}
		
		{\bf vlive-rs} \emph{https://github.com/drklee3/vlive-rs} \hfill {\bf April 2018 - Present} \\
			\vspace{-3.5mm}
			\begin{itemize} \itemsep -2pt
				\item {\bf Rust} library for livestreaming platform VLive's API.
				\item Implemented on the {\bf Hyper} client with Futures.
			\end{itemize}

		{\bf nuxt-yt} \emph{https://github.com/drklee3/nuxt-yt} \hfill {\bf June 2017 - September 2017} \\
			\vspace{-3.5mm}
			\begin{itemize} \itemsep -2pt
				\item Web app that automatically updates, aggregates, and tags YouTube videos based on certain criteria utilizing the YouTube Data API,
					with a search and video statistics.
				\item Uses {\bf Node.js}, {\bf Express} web framework, {\bf Nuxt.js} for server side 
					UI rendering, {\bf Vue.js} for frontend, and {\bf SQLite} for storing video data.
			\end{itemize}

		{\bf headphone-recommender} \hfill {\bf June 2017 - July 2017} \\
			\vspace{-3.5mm}
			\begin{itemize}	\itemsep -2pt
				\item Web app that analyzes MP3 files and recommends 100+ headphones based on price, form factor, and music sound signature.
				\item Uses {\bf Python} and the {\bf Flask} web framework.
			\end{itemize}
		
		{\bf gifgif} \hfill {\bf December 2016} \\
			\vspace{-3.5mm}
			\begin{itemize} \itemsep -2pt
				\item Application that trims, crops, and converts videos to gifs.
				\item Uses {\bf Electron}, {\bf Node.js} and FFmpeg.
			\end{itemize}

		\section{AWARDS}
		\vspace{6pt}

		{\bf City of Cupertino "Solve the Streets" Challenge Winner} \hfill {\bf January 2016} \\
			\vspace{-3.5mm}
			\begin{itemize} \itemsep -2pt
				\item Analyzed the traffic situation in the Silicon Valley and created a video addressing local traffic problems
					and proposing realistic and effective ways of improving transportation.
				\item Video edited and animated with Adobe After Effects.
			\end{itemize}

	\end{resume} 
\end{document}